Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-20 paper.tex
Use English spelling of bevaviour throughout.

First, we contacted multiple companies looking for production use of the Cog VM with memory intensive applications (>1Gb heaps) and built benchmarks out of one of the deployed applications. As an example, we will discuss in the paper in Section \ref{sec:mooseBench} the Moose benchmarks implemented with the help of Feenk\footnote{https://feenk.com/}. Part of the business of Feenk consists in analysing software written in multiple programming languages using the open-source framework Moose~\cite{MoosePaper1,MooseBook1}. Using Moose, the application parses the software to analyse into a model, performs analysis on it and lastly releases the model. Models currently used are encoded in up to 11Gb. This behavior was turned into three benchmarks, growing, accessing and shrinking the heap.

@@

To evaluate new full GC algorithms, we need to compare it against existing algorithms. Two of the most common GC algorithms are Mark-Compact and Mark-Sweep. We describe here the current Mark-Compact implementation, which has been in production for the past few years, and an implementation of Mark-Sweep we introduced as a reference earlier this year.  Cog is written to allow new object representations to be written and used.  Spur \cite{SpurMirandaBera} is the second object representation written for Cog.  Spur avoids the cost of an explicit read barrier to follow forwarding pointers on most accesses by handling the forwarding check on the failure side of cached dynamic message send; any send to a forwarded object will fail, and forwarding pointers in the current frame are followed on the failure side of lookup.  Hence in Spur all objects have room for a forwarding pointer.  This is key to the implementation of the Mark-Compact algorithm.

@@

\paragraph{Future work: stress GC tests.}
We can stress the garbage collector by running the configurable benchmarking tool with specific sets of options to test the memory startegy in edge cases. By increasing the amount of edge-cases benchmarks led on the garbage collector, we could infer a serie of tests to secure the garbage collector behavior in these situations.

>>>>

First, we contacted multiple companies looking for production use of the Cog VM with memory intensive applications (>1Gb heaps) and built benchmarks out of one of the deployed applications. As an example, we will discuss in the paper in Section \ref{sec:mooseBench} the Moose benchmarks implemented with the help of Feenk\footnote{https://feenk.com/}. Part of the business of Feenk consists in analysing software written in multiple programming languages using the open-source framework Moose~\cite{MoosePaper1,MooseBook1}. Using Moose, the application parses the software to analyse into a model, performs analysis on it and lastly releases the model. Models currently used are encoded in up to 11Gb. This behaviour was turned into three benchmarks, growing, accessing and shrinking the heap.

@@

To evaluate new full GC algorithms, we need to compare it against existing algorithms. Two of the most common GC algorithms are Mark-Compact and Mark-Sweep. We describe here the current Mark-Compact implementation, which has been in production for the past few years, and an implementation of Mark-Sweep we introduced as a reference earlier this year.

Cog is written to allow new object representations to be written and used.  Spur \cite{SpurMirandaBera} is the second object representation written for Cog.  Spur avoids the cost of an explicit read barrier to follow forwarding pointers on most accesses by handling the forwarding check on the failure side of cached dynamic message send; any send to a forwarded object will fail, and forwarding pointers in the current frame are followed on the failure side of lookup.  Hence in Spur all objects have room for a forwarding pointer.  This is key to the implementation of the Mark-Compact algorithm.

@@

\paragraph{Future work: stress GC tests.}
We can stress the garbage collector by running the configurable benchmarking tool with specific sets of options to test the memory startegy in edge cases. By increasing the amount of edge-cases benchmarks led on the garbage collector, we could infer a serie of tests to secure the garbage collector behaviour in these situations.
